Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
Final edit on result

Our model uses a weighted approach to estimate candidate support more
accurately by emphasizing higher-quality and more recent polls. The
weighting scheme integrates factors like poll recency, sample size,
pollster quality, and frequency, as inspired by the New York Times' methodology [@nyt_polling_averages] for polling averages.

@@

The linear regression models constructed for predicting support for
Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election
utilized both unweighted and weighted configurations. The model summary of support for Harris is shown in @tbl-summary1, and support for Trump is shown in @tbl-summary2. As shown in
@tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
estimated at 44.70% and 59.28% respectively in the unweighted models, while in weighted models, it's estimated at 45.2% and 54.8%,
represent their baseline support levels when all predictors are at
reference values. The high ( $R^2$ ) values of 0.824 for Harris’s
unweighted model and 0.892 for her weighted model, along with a similar
values of 0.849 and 0.916 for Trump, indicate that a significant portion
of the variation in support can be explained by the model's predictors.
The relatively low Root Mean Square Error (RMSE) values further suggest
that the models provide reasonably accurate predictions of support
levels.

>>>>

Our model uses a weighted approach to estimate candidate support more
accurately by emphasizing higher-quality and more recent polls. The
weighting scheme integrates factors like poll recency and sample size, which are
inspired by the New York Times' methodology [@nyt_polling_averages] for polling averages.

@@

The linear regression models constructed for predicting support for
Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election
utilized both unweighted and weighted configurations. The model summary of support for Harris is shown in @tbl-summary1, and support for Trump is shown in @tbl-summary2. As shown in
@tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
estimated at 44.70% and 51.87% respectively in the unweighted models, while in weighted models, it's estimated at 45.2% and 54.8%,
represent their baseline support levels when all predictors are at
reference values. The high ( $R^2$ ) values of 0.824 for Harris’s
unweighted model and 0.892 for her weighted model, along with a similar
values of 0.849 and 0.916 for Trump, indicate that a significant portion
of the variation in support can be explained by the model's predictors.
The relatively low Root Mean Square Error (RMSE) values further suggest
that the models provide reasonably accurate predictions of support
levels.
